A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface

### 2021-09-16 sections/appendix/descrete_event_simulation/main.tex
Add random seeds to python code

\begin{lstlisting}[style=pystyle]

    >>> import ambulance_game as abg
    >>> Simulation = abg.simulation.simulate_model(
    ...     lambda_1=3,
    ...     lambda_2=2,
    ...     mu=1,
    ...     num_of_servers=6,
    ...     threshold=10,
    ...     system_capacity=20,
    ...     buffer_capacity=10,
    ... )
    >>> all_records = Simulation.get_all_records()
    >>> all_records[3]
    Record(id_number=1, customer_class=0, node=2, arrival_date=0.4728763843239206, waiting_time=0.0, service_start_date=0.4728763843239206, service_time=0.5457131455415929, service_end_date=1.0185895298655134, time_blocked=0.0, exit_date=1.0185895298655134, destination=-1, queue_size_at_arrival=0, queue_size_at_departure=4)
\end{lstlisting}

@@

\begin{lstlisting}[style=pystyle]
    >>> import numpy as np
    >>> mean_wait = np.mean(
    ...    [record.waiting_time for record in all_records if record.node == 2]
    ... )
    0.2246928220731305
\end{lstlisting}

@@

\begin{lstlisting}[style=pystyle]
    >>> all_simulations = abg.simulation.get_multiple_runs_results(
    ...     lambda_1=3,
    ...     lambda_2=2,
    ...     mu=1,
    ...     num_of_servers=6,
    ...     threshold=10,
    ...     system_capacity=20,
    ...     buffer_capacity=10,
    ...     seed_num=0,
    ...     num_of_trials=10,
    ... )
    >>> mean_wait = np.mean(
    ...     [np.mean(w.waiting_times) for w in all_simulations]
    ... )
    0.35037759808989827
\end{lstlisting}

@@

To get the simulation object with all the data records, the following code can be
used:
\begin{lstlisting}[style=pystyle]
    >>> import ambulance_game as abg
    >>> Simulation = abg.simulation.simulate_model(
    ...     lambda_1=3,
    ...     lambda_2=2,
    ...     mu=1,
    ...     num_of_servers=6,
    ...     threshold=10,
    ... )
    >>> Simulation.get_all_records()[1]
    Record(id_number=1, customer_class=0, node=2, arrival_date=0.5391449803891563, waiting_time=0.0, service_start_date=0.5391449803891563, service_time=0.17003700443114755, service_end_date=0.7091819848203038, time_blocked=0.0, exit_date=0.7091819848203038, destination=-1, queue_size_at_arrival=0, queue_size_at_departure=0)
\end{lstlisting}

@@

\begin{lstlisting}[style=pystyle]
    >>> records = Simulation.get_all_records()
    >>> mean_wait = np.mean(
    ...     [w.waiting_time for w in records]
    ... )
    >>> mean_block = np.mean(
    ...     [b.time_blocked for b in records]
    ... )
    >>> mean_service = np.mean(
    ...     [s.service_time for s in records]
    ... )
    >>> target = 1
    >>> proportion_within_target = np.mean(
    ...     [w.waiting_time <= target for w in records]
    ... )

@@

\begin{lstlisting}[style=pystyle]
    >>> import numpy as np
    >>> import ambulance_game as abg
    >>> all_simulations = abg.simulation.get_multiple_runs_results(
    ...     lambda_1=3,
    ...     lambda_2=2,
    ...     mu=1,
    ...     num_of_servers=6,
    ...     threshold=10,
    ...     system_capacity=20,
    ...     buffer_capacity=10,
    ...     seed_num=0,
    ...     runtime=2000,
    ...     num_of_trials=10,
    ... )
    >>> mean_wait = np.mean([
    ...     np.mean(w.waiting_times) for w in mean_simulations
    ... ])
    >>> mean_service = np.mean([
    ...     np.mean(s.service_times) for s in mult_results
    ... ])
    >>> mean_block = np.mean([
    ...     np.mean(b.blocking_times) for b in mult_results
    ... ])
\end{lstlisting}

@@

\begin{lstlisting}[style=pystyle]
    >>> import ambulance_game as abg
    >>> (
    ...     overall_proportion,
    ...     class_1_proportion,
    ...     class_2_proportion,
    ... ) = abg.simulation.
    get_mean_proportion_of_individuals_within_target_for_multiple_runs(    
    ...     lambda_1=3,
    ...     lambda_2=2,
    ...     mu=1,
    ...     num_of_servers=6,
    ...     threshold=10,
    ...     system_capacity=20,
    ...     buffer_capacity=10,
    ...     seed_num=0,
    ...     num_of_trials=10,
    ...     runtime=2000,
    ...     target=1,
    ... )
\end{lstlisting}
% TODO: Fix code for proportion of individuals within time target

>>>>

\begin{lstlisting}[style=pystyle]
    >>> import ambulance_game as abg
    >>> Simulation = abg.simulation.simulate_model(
    ...     lambda_1=3,
    ...     lambda_2=2,
    ...     mu=1,
    ...     num_of_servers=6,
    ...     threshold=10,
    ...     system_capacity=20,
    ...     buffer_capacity=10,
    ...     seed_num=0,
    ... )
    >>> all_records = Simulation.get_all_records()
    >>> all_records[3]
    Record(id_number=1, customer_class=0, node=2, arrival_date=0.4728763843239206, waiting_time=0.0, service_start_date=0.4728763843239206, service_time=0.5457131455415929, service_end_date=1.0185895298655134, time_blocked=0.0, exit_date=1.0185895298655134, destination=-1, queue_size_at_arrival=0, queue_size_at_departure=4)

@@

\begin{lstlisting}[style=pystyle]
    >>> import numpy as np
    >>> mean_wait = np.mean(
    ...    [record.waiting_time for record in all_records if record.node == 2]
    ... )
    >>> mean_wait
    0.3608431242229529

@@

\begin{lstlisting}[style=pystyle]
    >>> all_simulations = abg.simulation.get_multiple_runs_results(
    ...     lambda_1=3,
    ...     lambda_2=2,
    ...     mu=1,
    ...     num_of_servers=6,
    ...     threshold=10,
    ...     system_capacity=20,
    ...     buffer_capacity=10,
    ...     seed_num=0,
    ...     num_of_trials=10,
    ... )
    >>> mean_wait = np.mean(
    ...     [np.mean(w.waiting_times) for w in all_simulations]
    ... )
    >>> mean_wait
    0.3566390561071839

@@

To get the simulation object with all the data records, the following code can be
used:
\begin{lstlisting}[style=pystyle]
    >>> import ambulance_game as abg
    >>> Simulation = abg.simulation.simulate_model(
    ...     lambda_1=3,
    ...     lambda_2=2,
    ...     mu=1,
    ...     num_of_servers=6,
    ...     threshold=10,
    ...     seed_num=0,
    ... )
    >>> Simulation.get_all_records()[4]
    Record(id_number=2, customer_class=0, node=2, arrival_date=0.5727571550618586, waiting_time=0.0, service_start_date=0.5727571550618586, service_time=0.7159547497671506, service_end_date=1.2887119048290092, time_blocked=0.0, exit_date=1.2887119048290092, destination=-1, queue_size_at_arrival=1, queue_size_at_departure=3)

@@

\begin{lstlisting}[style=pystyle]
    >>> records = Simulation.get_all_records()
    >>> mean_wait = np.mean(
    ...     [w.waiting_time for w in records]
    ... )
    >>> mean_wait
    0.23845862661827116

    >>> mean_block = np.mean(
    ...     [b.time_blocked for b in records]
    ... )
    >>> mean_block
    0.08501727452006658

    >>> mean_service = np.mean(
    ...     [s.service_time for s in records]
    ... )
    >>> mean_service
    0.7102610863960119

    >>> target = 1
    >>> proportion_within_target = np.mean(
    ...     [w.waiting_time <= target for w in records]
    ... )
    >>> proportion_within_target
    0.9387470071827614

@@

\begin{lstlisting}[style=pystyle]
    >>> import numpy as np
    >>> import ambulance_game as abg
    >>> all_simulations = abg.simulation.get_multiple_runs_results(
    ...     lambda_1=3,
    ...     lambda_2=2,
    ...     mu=1,
    ...     num_of_servers=6,
    ...     threshold=10,
    ...     system_capacity=20,
    ...     buffer_capacity=10,
    ...     seed_num=0,
    ...     runtime=2000,
    ...     num_of_trials=10,
    ... )
    >>> mean_wait = np.mean([
    ...     np.mean(w.waiting_times) for w in all_simulations
    ... ])
    >>> mean_wait
    0.35585979549204577

    >>> mean_service = np.mean([
    ...     np.mean(s.service_times) for s in all_simulations
    ... ])
    >>> mean_service
    1.002184850213415

    >>> mean_block = np.mean([
    ...     np.mean(b.blocking_times) for b in all_simulations
    ... ])
    >>> mean_block
    0.3976966024549059

@@

\begin{lstlisting}[style=pystyle]
    >>> import numpy as np
    >>> (
    ...     overall_proportion,
    ...     class_1_proportion,
    ...     class_2_proportion,
    ... ) = abg.simulation.get_mean_proportion_of_individuals_within_target_for_multiple_runs(    
    ...     lambda_1=3,
    ...     lambda_2=2,
    ...     mu=1,
    ...     num_of_servers=6,
    ...     threshold=10,
    ...     system_capacity=20,
    ...     buffer_capacity=10,
    ...     seed_num=0,
    ...     num_of_trials=10,
    ...     runtime=2000,
    ...     target=1,
    ... )
    >>> np.mean(overall_proportion)
    0.45785790578122043

    >>> np.mean(class_1_proportion)
    0.4406768928300989

    >>> np.mean(class_2_proportion)
    0.4840634188366037

\end{lstlisting}
% TODO: Fix code for proportion of individuals within time target
